Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-04-26 numerical-amr.tex
one additional edit.

Each grid patch in \enzo\ contains arrays of values for baryon and particle quantities.   Grids are partitioned into a core of \emph{real zones} and a surrounding layer of \emph{ghost zones}, as shown in Figure~\ref{fig:amr_hierarchy}.  The real zones store field values and ghost zones are used to temporarily store values that have been obtained directly from neighboring grids or interpolated from a parent grid.  These zones are necessary to accommodate the computational stencil of the (magneto)hydrodynamics solvers (Sections~\ref{sec.hydro.ppm} and~\ref{sec.hydro.zeus}) and the gravity solver (section~\ref{sec.gravity}).  The PPM and Zeus hydro solvers require 3 layers of ghost zones,  and the gravity solver requires 6 (although only for the density and potential fields).  This can lead to significant memory and computational overhead, particularly for smaller grid patches at high levels of refinement.

>>>>

Each grid patch in \enzo\ contains arrays of values for baryon and particle quantities.   Grids are partitioned into a core of \emph{real zones} and a surrounding layer of \emph{ghost zones}, as shown in Figure~\ref{fig:amr_hierarchy}.  The real zones store field values and ghost zones are used to temporarily store values that have been obtained directly from neighboring grids or interpolated from a parent grid.  These zones are necessary to accommodate the computational stencil of the (magneto)hydrodynamics solvers (Sections~\ref{sec.hydro.ppm} and~\ref{sec.hydro.zeus}) and the gravity solver (Section~\ref{sec.gravity}).  The PPM and Zeus hydro solvers require 3 layers of ghost zones,  and the gravity solver requires 6 (although only for the density and potential fields).  This can lead to significant memory and computational overhead, particularly for smaller grid patches at high levels of refinement.
